---
title: "Abnormal Bond Returns and Dividend Announcements Analysis"
output: word_document
date: "2023-06-16"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,message = FALSE, warning = FALSE)
```

## Loading Libraies and Data
```{r}
library(readxl)
library(readr)
library(tidyverse)
library(zoo)

# Loading Data
df1<-read_excel("C:\\Users\\user\\Downloads\\Bond_Fundamentals_final-1.xlsx")
df2<-read_excel("C:\\Users\\user\\Downloads\\DividendAnnouncements.xlsx")
# Loading and Cleaning the trace price dataset
csv_lines <- readLines("C:\\Users\\user\\Downloads\\trace_daily_r_CP.csv")
split_lines <- strsplit(csv_lines, ",")
num_columns <- max(lengths(split_lines))
df <- data.frame(matrix(ncol = num_columns, nrow = length(split_lines), dimnames = list(NULL, paste0("V", 1:num_columns))))
for (i in 1:length(split_lines)) {
  df[i, 1:length(split_lines[[i]])] <- split_lines[[i]]
}

```

## Data Cleaning and Preprocessing

```{r}
# Remove unnecessary rows
df<-df[,-1]
df1<-df1[,-1]

# Define a list of new column names
new_column_names <- c("cusip_id", "trd_exctn_dt", "TWP", "TWY", "vol_day", "n_day", "maturity", "PERMNO", "RATING_SPR", "RATING_FR", "RATING_MR", "moody_numeric", "sp_numeric", "fitch_numeric", "RTNG")

# Assign the new column names to the data frame
colnames(df) <- new_column_names


# Removev missing values
df<-df[-1,]
# Remove quotation marks from cusip_id and RTNG columns
df$cusip_id <- gsub("\"", "", df$cusip_id)
df$RTNG <- gsub("\"", "", df$RTNG)
df$RATING_SPR <- gsub('"', '', df$RATING_SPR)
df$RATING_FR <- gsub('"', '', df$RATING_FR)
df$RATING_MR <- gsub('"', '', df$RATING_MR)
df$moody_numeric <- gsub('"', '', df$moody_numeric)
df$sp_numeric <- gsub('"', '', df$sp_numeric)
df$fitch_numeric <- gsub('"', '', df$fitch_numeric)
colnames(data[,9:14])
# Convert "NA" strings to missing values
df[df == "NA"] <- NA

data <- df[complete.cases(df), ]
head(data)  # Print the data frame with updated column names


# Merge datasets
merged_data <- merge(data, df1, by = c("cusip_id"))
# Change column name from 'ID' to 'Organization of Risk PermID'
colnames(df2)[colnames(df2) == "ID"] <- "Organization of Risk PermID"
# Add the dividend announcement to data
merged_data <- merge(merged_data, df2, by = c("Organization of Risk PermID"))

# Filter bonds that are not rated
filtered_data <- merged_data[!is.na(merged_data$RTNG), ]

# Consider trades of institutions with trade volume >= 100k
filtered_data <- filtered_data[filtered_data$vol_day >= 100000, ]
# Convert "TWP" column to numeric
filtered_data$TWP <- as.numeric(filtered_data$TWP)
# Convert "TWP" column to numeric
filtered_data$TWP <- as.numeric(filtered_data$TWP)
filtered_data$n_day <- as.numeric(filtered_data$n_day)
# Calculate bond returns using "n_day" as a substitute for "AAI"
filtered_data$returns <- with(filtered_data, (TWP - lag(TWP) + n_day) / lag(TWP))


# Calculate PBR. Apply the mean-adjusted return model
filtered_data$PBR <- filtered_data$returns - filtered_data$`Dividend Amount`
# Calculate the mean expected excess return (EBR)
estimation_period <- 5  # Number of periods for EBR calculation
filtered_data <- filtered_data %>%
  group_by(cusip_id) %>%
  arrange(trd_exctn_dt) %>%
  mutate(EBR = rollmean(PBR, k = estimation_period, fill = NA, align = "right", na.rm = TRUE))

# Calculate the abnormal bond return (ABR)
filtered_data$ABR <- filtered_data$PBR - filtered_data$EBR
```

## Data Analysis
```{r}
# Step 1: Create matching portfolios based on bond ratings and time-to-maturity

# Using Lehman Brothers indexes as benchmarks
matching_portfolios <- filtered_data %>%
  group_by(RTNG, maturity) %>%
  summarise(average_PBR = mean(PBR, na.rm = TRUE))  # Adjust as per your specific methodology


# Step 2: Calculate the expected return (EBR) for each bond based on the matching portfolios

# Using the matching portfolios as the reference
filtered_data <- filtered_data %>%
  left_join(matching_portfolios, by = c("RTNG", "maturity")) %>%
  mutate(EBR = ifelse(!is.na(average_PBR), average_PBR, NA))  # Assign EBR from matching portfolios, NA if no match


# Step 3: Calculate the abnormal bond return (ABR)

filtered_data$ABR <- filtered_data$PBR - filtered_data$EBR


# Step 4: Analyze the correlation between dividend announcements and abnormal bond returns
# Remove NA from the "ABR" column
filtered_data_no_na <- filtered_data[complete.cases(filtered_data$ABR), ]
# correlation analysis
correlation <- cor(filtered_data_no_na$`Dividend Amount`, filtered_data_no_na$ABR)
# Perform statistical tests such as Corrado-Test to test the significance of abnormal returns

# Print correlation result
cat("Correlation between dividend announcements and abnormal bond returns:", correlation, "\n")

# Perform the Corrado Test

# Step 1: Fit a regression model to estimate abnormal returns
model <- lm(ABR ~ `Dividend Amount`, data = filtered_data_no_na)

# Step 2: Extract the coefficients and standard errors from the model
coefficients <- coef(model)
std_errors <- summary(model)$coefficients[, "Std. Error"]

# Step 3: Perform hypothesis testing to assess the significance of abnormal returns
t_statistic <- coefficients["`Dividend Amount`"] / std_errors["`Dividend Amount`"]
p_value <- 2 * pt(-abs(t_statistic), df = model$df.residual)

# Step 4: Print the results
cat("Corrado Test Results:\n")
cat("Estimate:", coefficients["`Dividend Amount`"], "\n")
cat("Standard Error:", std_errors["`Dividend Amount`"], "\n")
cat("t-value:", t_statistic, "\n")
cat("p-value:", p_value, "\n")

# Perform T-Test
t_test <- t.test(filtered_data_no_na$ABR)
cat("T-Test Results:\n")
print(t_test)
```

The Corrado test's results are as follows:

Estimate: The "Dividend Amount" variable's estimated coefficient is -0.9998212. This suggests that, on average, a one-unit increase in the dividend amount corresponds to a fall in the anomalous returns of about -0.9998212.

Standard Error: The "Dividend Amount" coefficient's standard error is 0.0006172603. The estimated coefficient's accuracy or degree of uncertainty is represented by this. More accurate estimations are shown by smaller standard errors.

t-value: The "Dividend Amount" coefficient's t-value is -1619.772. It is obtained by subtracting the standard error from the estimated coefficient. The t-value assesses the coefficient's significance and evaluates if it deviates statistically from zero. The t-value in this instance is extremely high, showing a significant correlation between  between the dividend amount and abnormal returns.

The stated p-value is zero, which is less than the usual significance level of 0.05. If the null hypothesis (no relationship) is true, the p-value indicates the likelihood of seeing a t-value as extreme as -1619.772 or more extreme. With a p-value of 0, there is strong evidence to reject the null hypothesis and draw the conclusion that the dividend amount and anomalous returns are significantly correlated.

In conclusion, the Corrado test results show that the association between the dividend amount and anomalous returns is quite significant. According to the computed coefficient, smaller abnormal returns are linked to greater dividend amounts. Strong proof of the relationship's statistical significance is provided by its small standard error, high t-value, and extremely low p-value.

